Regular singular Volterra equations on complex domains

### 2023-07-28 reg-sing-volterra.tex
Add motivating example
Also work on regularity result for prototype solution, add conditions to
propositions, and add some references.

%%\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{rmk}{Remark}
\newtheorem{lemma}{Lemma}

@@

If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
\subsection{Setting}\label{setting}
\subsubsection{The domain}\label{setting:domain}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$. For some of our results, we'll need an extra condition on $\domain$:
\begin{itemize}
\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$. In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$. Since $\domain$ doesn't contain $\zeta = 0$, we'll always leave that starting point out of the path.
\end{itemize}
For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
\end{tikzpicture}
\end{center}
\subsubsection{The prototype operator}\label{setting:basic}
The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.

Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
\[ \hardker(a, a') = \textcolor{magenta}{-} \frac{q(a')}{p(a)}, \]
where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means that for some constant $\tau$---the {\em residue} of the singularity---the difference
\[ \hardker(a, a') \textcolor{magenta}{-} \frac{\tau}{\zeta(a)} \]
is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\Omega^2$. We'll assume that $\tau$ is real and positive.

Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
\begin{verify}
[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded. By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition. Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
\end{verify}
For some of our results, we'll also need to keep $|p|$ and $|q|$ under control as $|\zeta|$ goes to infinity.
\begin{itemize}
%%\item[($\text{\textsc{slow}} \mid \lambda_0$)]
\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
\begin{align*}
\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
\end{align*}
outside some neighborhood of $\zeta = 0$ in $\Omega$. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point. The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
\end{itemize}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
\subsubsection{The perturbed operator}\label{setting:perturbed}
\color{RoyalBlue}
We'll generalize $\hardpart$ by adding a perturbation $\softpart$ that doesn't have a separable kernel, but does have a smoothing effect that counteracts the singularity of $\hardpart$. To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\epsilon > 0$ on the diagonal in $\Omega^2$. This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $p(a)^{-1}$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:slow} on $p$ and $q$. Altogether, we'll require:
\begin{itemize}
\condconst{diag}{\epsilon, \lambda}\label{cond:eps-lambda} We have
\[ \big| k_\text{extra} (a, a') \big| \lesssim \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{itemize}
\color{black}

Our ultimate goal is the study of certain integral equations where the integral kernel is a perturbation of $k_\text{basic}$. In particular, we are interested in holomorphic Volterra operators $\volterra=\hardpart+\softpart$, hence the kernel $k_\text{extra}$ of $\softpart$ is a holomorphic function on $\Omega^2$.

@@

Notice that if $a$ and $a'$ are close to $\zeta=0$, then the exponential factor is bounded and $k_\text{extra}(a,a')$ goes like $|\zeta(a)|^{\epsilon-1}$. Conversely, as $|\zeta(a)|$ goes to infinity (far from $\zeta=0$), the exponential term will be dominant because the polynomial growth of $|\zeta(a)|^{\epsilon-\tau}$ can be bounded by $e^{|\zeta(a)|}$.
\subsection{Main results}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\begin{thm}\label{thm:basic_volterra}
For a regular singular Volterra equation
\[ f = \hardpart f \]
involving the kind of operator described in Section~\ref{setting:basic}, we have the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to $0$. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
\end{thm}
\begin{thm}
Suppose $\hardpart$ satisfies Condition~\eqref{cond:slow} from Section~\ref{setting:basic}. Then the solution $f_0$ from Theorem~\ref{thm:basic_volterra} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly'']}. In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
\begin{thm}\label{thm:perturbed_volterra}
\textcolor{DarkTurquoise}{Existence and uniqueness for perturbed operator}
Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
\[ f = \Big[\hardpart +\softpart \Big] f + g \]
given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}. 
\end{thm}
%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

@@

%%Under these conditions, let's try to solve the regular singular Volterra equation
%%\[ \mathcal{V}f = 0. \]
%%The leading-order part of the equation,
%%\[ \big[p_1 \zeta + \partial^{-1} \circ q_0\big]f = 0, \]
%%has $\zeta^{\tau-1}$ as a solution, where $\tau = p_1/q_0$. If we guess that the function spaces defined in Section~\ref{fn-spaces} are well suited for this problem, we might hope for the full equation to have a solution of the form
%%\[ f = \zeta^{\tau-1} + f_*, \]
%%where $f_* \in \holoL{\infty, 1-\tau-\epsilon}_Z(\Omega)$ for some $Z \in \C$. When $Z\Omega$ is in the right half-plane and $|Z|$ is large enough, there is in fact a unique solution of this form.
%%\end{thm}
\section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
\subsection{Weighted holomorphic $L^\infty$ spaces}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\cont(\Omega)$ be the space of continuous complex-valued functions on $\Omega$. Give $\cont(\Omega)$ the compact-open topology, recalling that this is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}. The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}\textcolor{orange}{[Luecking \& Rubel]}.

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.

\section{Construction and regularity of the prototype solution}

\subsection{Construction}\label{sec:construction}

\begin{prop}
    Let $b\in\Omega$, the function 
    \begin{equation}%%\label{eqn:test_solution}
    f_0(a)=\frac{p(b)}{p(a)} \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]
   \end{equation}
is a solution of the Volterra equation $\hardpart f_0=f_0$. We call $f_0$ a prototype solution.  
\end{prop}

\begin{proof}
    Let $\Psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \Psi_0 = - \frac{q}{p} \Psi_0 d\zeta $. Hence, for every $a\in\Omega$ 
    \begin{align*}
        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\Psi_0 d\zeta \\
        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \Psi_0 d\zeta\\
        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\Psi_0  \\
    \end{align*}
    Now we claim $\lim_{a\to 0}\Psi_0(a)=0$: in fact,
    \begin{align*}
        \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert&\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\Big \vert\, |d\zeta|\right)\\
        &\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\textcolor{magenta}{-}\frac{\tau}{\zeta}\Big \vert\, |d\zeta| + \tau \int_b^a\frac{|d\zeta|}{|\zeta|} \right)\\
        &\Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\left(\int_b^a \Big\vert\frac{q}{p}\textcolor{magenta}{-}\frac{\tau}{\zeta}\Big \vert\, |d\zeta|  \right)
    \end{align*}
    and by \textcolor{orange}{[limit assumption]}
\begin{align*}
     \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert& \leq \Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\Big(c |\zeta(a)-\zeta(b)|\Big)\\
     &\leq C |\zeta(a)|^\tau e^{c|\zeta(a)|}
\end{align*}
 which ends the proof of the claim. We deduce that $\hardpart  f_0=f_0 $. 
\end{proof}

\subsection{Asymptotics}\label{sec:asymptotics}

\begin{prop}
    Let $b\in\Omega$ and $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $f_0\in\singexp{\tau-1}{\lambda}(\Omega)$ with $\tau$ and $\lambda$ defined as in {\tt setting}

\end{prop}

>>>>

%%\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{rmk}{Remark}

@@

If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}

\subsection{Setting}\label{setting}
\subsubsection{The domain}\label{setting:domain}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$. For some of our results, we'll need an extra condition on $\domain$:
\begin{itemize}
\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$. In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$. Since $\domain$ doesn't contain $\zeta = 0$, we'll always leave that starting point out of the path.
\end{itemize}
For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
\end{tikzpicture}
\end{center}
\subsubsection{The prototype operator}\label{setting:basic}
The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.

Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
\[ \hardker(a, a') = \textcolor{magenta}{-} \frac{q(a')}{p(a)}, \]
where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
\begin{itemize}
\condconst{sing}{\tau}\label{cond:sing} For some constant $\tau$---the {\em residue} of the singularity---the difference
\[ \hardker(a, a') \textcolor{magenta}{-} \frac{\tau}{\zeta(a)} \]
is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
\end{itemize}
We'll assume that $\tau$ is real and positive.

Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
\begin{verify}
[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded. By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition. Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
\end{verify}
For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
\begin{itemize}
\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
\begin{align*}
\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
\end{align*}
outside some neighborhood of $\zeta = 0$ in $\Omega$. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point. The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
\end{itemize}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
\begin{itemize}
\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} We can find a constant $\lambda_\Delta$ with
\[ \big| \hardker(a, a') \big| \textcolor{magenta}{\lesssim} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
\end{itemize}
\subsubsection{The perturbed operator}\label{setting:perturbed}
We'll generalize $\hardpart$ by adding a perturbation $\softpart$ that doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}). To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\epsilon > 0$ on the diagonal in $\Omega^2$. This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$. Altogether, we'll require:
\begin{itemize}
\condconst{diag}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
\[ \big| k_\text{extra} (a, a') \big| \lesssim \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{itemize}
Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.
\color{RoyalBlue}
Our ultimate goal is the study of certain integral equations where the integral kernel is a perturbation of $k_\text{basic}$. In particular, we are interested in holomorphic Volterra operators $\volterra=\hardpart+\softpart$, hence the kernel $k_\text{extra}$ of $\softpart$ is a holomorphic function on $\Omega^2$.

@@

Notice that if $a$ and $a'$ are close to $\zeta=0$, then the exponential factor is bounded and $k_\text{extra}(a,a')$ goes like $|\zeta(a)|^{\epsilon-1}$. Conversely, as $|\zeta(a)|$ goes to infinity (far from $\zeta=0$), the exponential term will be dominant because the polynomial growth of $|\zeta(a)|^{\epsilon-\tau}$ can be bounded by $e^{|\zeta(a)|}$.
\color{black}
\subsection{Main results}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\begin{thm}\label{thm:basic_volterra}
\textcolor{orange}{[Assume the domain $\domain$ satisfies {\em Condition \eqref{cond:star}}] from Section \ref{setting:domain}}.
Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
\[ f = \hardpart f \]
have the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to zero. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
\end{thm}
\begin{proof}
Section~\ref{sec:proto-construction-regularity}. Proposition~\ref{prop:construction} shows that $f_0$ is a solution, and Proposition~\ref{prop:asymptotic at zero} shows that it scales as desired as $\zeta$ goes to zero.
\end{proof}
\begin{thm}\label{thm:proto-growth}
\textcolor{orange}{[Assume the domain $\domain$ satisfies {\em Condition \eqref{cond:star}}] from Section \ref{setting:domain}}. Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:slow}} from Section~\ref{setting:basic}. Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly'']}. In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
\begin{lemma}\label{thm:perturbed_volterra}
Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
\[ f = \Big[\hardpart +\softpart \Big] f + g \]
given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}. 
\end{lemma}

\begin{thm}\label{thm:general_volterra}
    Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}. Then the Volterra equation 
    \[f = \left[ \hardpart + \softpart \right] f\]
    admits a unique solution in the affine subspace
\[ f_0 + \singexp{\tau-1+\epsilon}{{\Lambda}}(\Omega) \]
of the function space $\singexp{\tau-1+\epsilon}{{\Lambda}}(\Omega)$, defined in Section~\ref{fn-spaces}, for $\Lambda$ ``big enough'' (meaning $\Lambda>\lambda_\Delta$, and we may require $\Lambda \gg \lambda_\Delta$). The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
\end{thm}
%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

@@

%%Under these conditions, let's try to solve the regular singular Volterra equation
%%\[ \mathcal{V}f = 0. \]
%%The leading-order part of the equation,
%%\[ \big[p_1 \zeta + \partial^{-1} \circ q_0\big]f = 0, \]
%%has $\zeta^{\tau-1}$ as a solution, where $\tau = p_1/q_0$. If we guess that the function spaces defined in Section~\ref{fn-spaces} are well suited for this problem, we might hope for the full equation to have a solution of the form
%%\[ f = \zeta^{\tau-1} + f_*, \]
%%where $f_* \in \holoL{\infty, 1-\tau-\epsilon}_Z(\Omega)$ for some $Z \in \C$. When $Z\Omega$ is in the right half-plane and $|Z|$ is large enough, there is in fact a unique solution of this form.
%%\end{thm}

\subsection{Acknowledgements}

This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.

We thank Fondation Mathematique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.

\section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
\subsection{Weighted holomorphic $L^\infty$ spaces}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\cont(\Omega)$ be the space of continuous complex-valued functions on $\Omega$. Give $\cont(\Omega)$ the compact-open topology, recalling that this is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}. The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}.

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{Solving holomorphic Volterra equations}
\subsection{Overview}
\subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}

\subsubsection{Construction}\label{sec:construction}

\begin{prop}\label{prop:construction}
    Let $b\in\Omega$, the function 
    \begin{equation}%%\label{eqn:test_solution}
    f_0(a)=\frac{p(b)}{p(a)} \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]
   \end{equation}
is a solution of the Volterra equation $\hardpart f_0=f_0$. We call $f_0$ a prototype solution.  
\end{prop}

\begin{proof}
    Let $\psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \psi_0 = -\frac{q}{p} \psi_0\;d\zeta $. Hence, for every $a\in\Omega$ 
    \begin{align*}
        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\psi_0 d\zeta \\
        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0 d\zeta\\
        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\psi_0  \\
    \end{align*}
    \textcolor{orange}{Bring the proof of Proposition~\ref{prop:asymptotic at zero} in here. Prove Proposition~\ref{prop:asymptotic at zero} by noting that our argument that $\lim_{\zeta(a) \to 0} \psi_0(a) = 0$ actually proves something stronger.}
    \color{RoyalBlue}
    Now we claim $\lim_{a\to 0}\psi_0(a)=0$: in fact,
    \begin{align*}
        \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert&\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\Big \vert\, |d\zeta|\right)\\
        &\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\textcolor{magenta}{-}\frac{\tau}{\zeta}\Big \vert\, |d\zeta| + \tau \int_b^a\frac{|d\zeta|}{|\zeta|} \right)\\
        &\Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\left(\int_b^a \Big\vert\frac{q}{p}\textcolor{magenta}{-}\frac{\tau}{\zeta}\Big \vert\, |d\zeta|  \right)
    \end{align*}
    and by Condition \eqref{cond:sing}
\begin{align*}
     \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert& \leq \Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\Big(c |\zeta(a)-\zeta(b)|\Big)\\
     &\leq C |\zeta(a)|^\tau e^{c|\zeta(a)|}
\end{align*}
 which ends the proof of the claim.\color{black} We deduce that $\hardpart  f_0=f_0$. 
\end{proof}

\subsubsection{Regularity}\label{sec:asymptotics}

\begin{prop}\label{prop:asymptotic at zero}
    \textcolor{orange}{Assume $\domain$ satisfies Condition~\eqref{cond:star}.} Let $b\in\Omega$ and $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $f_0\in\singexp{\tau-1}{\lambda}(\Omega)$ with $\tau$ and $\lambda$ defined as in {\tt setting}
\end{prop}
